HO unification from object language to meta language

### 2024-03-22 paper/main.tex
wip

\section[Compilation: fo\_tm to tm]{Basic compilation \Fo{} to \Ho{}}
\label{sec:compilation}

In this section we describe a basic compilation scheme that we refine
later, in the following sections.

The objective of the compilation is to recognize the higher-order variables
available in \Ho{} when expressed in a first order way in \Fo{}. The compiler
also generates a list of links that are used to bring back the substitution from
\Ho{} to \Fo{} and allocates in the memory a cell for each variable.

types
\input{code/comp_base_types}

core

@@

aux

@@

\subsection{Problems with $\eta$}

@@

\subsection{Problems with $\beta$}

>>>>

\section[Compilation: fo\_tm to tm]{Basic simulation of \Fo{} in \Ho{}}
\label{sec:compilation}

In this section we describe a basic compilation scheme that we refine
later, in the following sections. This scheme is sufficient to implement
an \Uo{} that respects $\beta$-conversion for terms in \llambda. The extension to
$\eta\beta$-conversion is described in Section \ref{sec:eta} and the support
for terms outside \llambda in Section \ref{sec:beta}.

The objective of the compilation is to recognize the higher-order variables
available in \Ho{} when expressed in a first order way in \Fo{}. The compiler
also generates a map to bring back the substitution from
\Ho{} to \Fo{}.

\newtheorem{invariant}{Invariant}

\input{code/comp_base_types}

\begin{invariant}[Unification variable arity] Each variable \elpiIn{A}
in \Ho has a (unique) arity \elpiIn{N} and each occurrence~
\elpiIn{(uvar A L)} is such that \elpiIn{(len L N)} holds
\end{invariant}

\noindent The arity of a variable in \Ho (a \elpiIn{hvariable} is stored in
the mapping. In particular \elpiIn{m-alloc}
bla bla explain. Multiple mappings for the same \elpiIn{fvariable}
are handled in section \ref{sec:eta}.

\input{code/alloc_mapping}

The signature of the \elpiIn{comp} predicate below allows for the generation of
links (suspended unification problems) that play no role in this section
but play a major role in Sections \ref{sec:eta} and \ref{sec:beta}.

@@

This preliminary version of \elpiIn{comp} simply recognizes \Fo variables
applied to a (possibly empty) duplicate free list of names (i.e.
\elpiIn{pattern-fragment} detects variables in \llambda).

The auxiliary function \elpiIn{close-liks}

@@

\subsection{Problems with $\eta$}\label{sec:eta}

@@

\subsection{Problems with $\beta$}\label{sec:beta}
